Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Typo
Minor typos and additions.

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. Since the observed
characteristics of these subjects are very similar, similarity of their
unobserved characteristics is often credible as well, and differences in the
outcomes between the treated and untreated can be plausibly attributed to the
treatment alone. As a practical matter this involves comparing units within a
bandwidth just above and just below the threshold.

@@

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.

@@

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{+,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
\intertext{and}
  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum[+]{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_+(b,i)} / b).
\end{align*}
The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
``$-$'' for ``$+$.''

>>>>

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. Since the observed
characteristics of these subjects are very similar, similarity of their
unobserved characteristics is often credible as well, and differences in the
outcomes between the treated and untreated can be plausibly attributed to the
treatment alone. As a practical matter this involves comparing units within a
bandwidth just above and just below the threshold.

@@

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.

@@

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{+,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
\intertext{and}
  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_+(b,i)} / b).
\end{align*}
The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
``$-$'' for ``$+$.''
